Comparison of methods test

### 2019-05-02 index.Rmd
testing dummy markdown

---
title: "Comparison of methods"
output: html_document
---

knit: (function(input_file, encoding) {
  out_dir <- 'docs';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, 'index.html'))})

>>>>

---
title: "Comparison of methods test"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
